---
title: "Fry Analysis"
author: "FBJ"
date: "2024-05-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(rgdal)
```

```{r}
library(sp)
```

```{r}
library(sf)
```

#import vector shapefile containing deposit locations

```{r}
au_locs<-  st_read("C:/Users/user/OneDrive/Documents/Git/Fry/Gold_occurrences.shp")
```

```{r}
str(au_locs)
```

```{r}
head(au_locs)
```

```{r}
x<- au_locs$x
```

```{r}
y <- au_locs$y
```

```{r}
data <- data.frame(x,y)
```

```{r}
head(data)
```

#create vector to store ouptut

```{r}
result_x <- c()
```

```{r}
result_y <- c()
```

# Loop through each record in x and y to perform the subtraction using each location as the centre point

```{r}        
for (i in 1:nrow(data)) {
  for (j in 1:nrow(data)) {
    diff_x <- data$x[i] - data$x[j]
    diff_y <- data$y[i] - data$y[j]
      if (!(diff_x == 0 && diff_y == 0)) {
      result_x <- c(result_x, diff_x)
      result_y <- c(result_y, diff_y)
    }
 }
}
```

#centering the fry points on the original gold occurrences

```{r}
fry_pts <- data.frame(x = result_x+mean(data$x), y = result_y+mean(data$y))
```

#convert fry points to a spatial feature

```{r}
fry_pts_sp <- st_as_sf(fry_pts, coords = c("x", "y"))
```

#assign coordinate system to the fry points shapefile

```{r}     
st_crs(fry_pts_sp) <- st_crs(au_locs)
```

```{r}
str(fry_pts_sp)
```

#plot the original gold occurrences and the fry points

```{r}
library(ggplot2)
```

```{r}
ggplot()+
  theme_bw()+
  theme(panel.grid.major = element_blank())+
  geom_sf (data=au_locs, aes(col="black"))+
  geom_sf(data=fry_pts_sp, aes(col="red"))+
  scale_color_identity(labels=c(black="Gold Occurrences", red="Fry Points"), guide="legend")+
   theme(plot.title = element_text(hjust= 0.5))+
  theme(axis.text.y = element_text(angle = 88))+
  ggtitle ("Fry Plot")+
  coord_sf()
```
